\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{mathpazo}
\usepackage{probsoln}
\usepackage{color}


\title{}
\author{Qingyue Zhu }
\date{May 2017}

\usepackage{natbib}
\usepackage{graphicx}

\begin{document}

\maketitle

\section*{Problem Definition}
\subsection*{History of the Problem}
Sometimes people get a product which has cheaper price in another store. And people want to get the same product in cheaper price.

\subsection*{Why this problem interesting}
This problem is interesting, because this problem is related to the real life, and most of the people have this problem. 

\subsection*{When and why does the problem occur}
This problem occur since people start to buy products and realize there is another store which has the same product with lower price. And most of people want to save money, so this problem occur.

\subsection*{Is the problem already solved? What is done now?}
This problem can be solved by people search from internet and shop by shop to compare the price for the same product. Or people can buy products from online shop. But this does not solve the problem all, because the process is still complicate. And the online shopping also cannot solve all the problem, because people still need to buy groceries and fresh foods like vegetables and fruits.

\subsection*{Are there similar system or solution to the one we propose}
Right now, prices only provided by the shop. And people need to search for different store to solve the problem. The solution we propose is to combine the prices for the shops together, which makes the whole process easier for users.

\subsection*{Are there possible improvements to current solutions?}
The improvement is that all the information should combined together and makes that easier for users, which is the solution that we propose.

\section*{Proposed Solution}
\subsection*{What does this project achieve?}
This project will make user easier to find the products' information and compare with the price for different stores.

\subsection*{What will the project produce?}
This project will be a website that can search for the prices and more information for products.
\color{red}
This need to add more information.
\color{black}
\subsection*{relative detail}
Project will produce the detail information for the detail in every include store. For example, user can search a product by key words like shampoo. And every include brand for shampoo will display. User can find which store contain that specific product and prices in different stores.

\end{document}
